\documentclass[12pt]{article}
\usepackage[margin=1in]{geometry} % change margins
\usepackage{graphicx} % inserting images
\usepackage{caption} % captions
\usepackage{amsmath} % for better math
\usepackage{verbatim} %used for comment blocks
\usepackage{mathtools}
\usepackage[english]{babel}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage{placeins}
\usepackage[square, sort, numbers]{natbib}
\usepackage{url}
\usepackage{setspace}
\usepackage{breqn}
\usepackage{subcaption}
\usepackage{textcomp}
\usepackage{float}
\usepackage{leftidx}
\usepackage{bm}
\usepackage[titletoc,toc, title]{appendix}
\usepackage[utf8]{inputenc}
\usepackage{diagbox}
\usepackage{hyperref}
\usepackage{tcolorbox}

\usepackage{amsmath,amssymb,braket,cancel,nicefrac,physics,tensor,slashed}
\usepackage{color,empheq,enumitem,forloop,graphicx,microtype,subcaption,verbatim,wrapfig,pdfpages,titlesec}
\usepackage{array,booktabs,multicol,multirow,tabularx} 

\usepackage{fancyhdr}
\addto\captionsenglish{\renewcommand{\chaptername}{Lab}}

\def\cesar#1{{\color{blue}[#1]}}
\def\anhkhoi#1{{\color{olive}[#1]}}
\def\nik#1{{\color{red} [#1]}}

\tcbset{colback=blue!5!white,colframe=blue!75!black,center,halign=justify,width=0.9\textwidth,fonttitle=\bfseries}

\pagenumbering{gobble}
\linespread{1}
\title{Log Book}
\date{}

\begin{document}

\maketitle

\begin{table}[h]
\begin{tabular}{c | c}
Student ID number & Name \hspace{6cm} \\ \hline
\hspace{4cm} & \\
\hspace{4cm} & \\
\hspace{4cm} & \\
\hspace{4cm} & \\
\hspace{4cm} & \\
\end{tabular}
\end{table}

\begin{table}[h]
\begin{tabular}{l c l c}
\textbf{Lab:} & \hspace{6.5cm} & \textbf{Date \&} & \\
\textbf{Session:} & & \textbf{Session Period:} & 
\end{tabular}
\end{table}

\noindent You may print as many additional blank pages as necessary for each section.
You may use the back side of each sheet.	
Be sure to number the pages and place them in the correct ordering.

\section{Pre-lab Activity}
Answer your pre-lab questions here.
\newpage 

\section{Introduction}
Clearly state your \textbf{goals and hypotheses}.
\newpage

\section{General Notes}
This section may be less organized. We expect to find: a rough protocol, rough calculations
and thoughts about your intermediate results.
This section is expected to be ``messy".
\newpage

\section{Results}
Formally present your results. See the \textbf{Data Presentation} section of your lab manual.

\newpage

\section{Conclusion}
Summarize your findings, and offer an improvement to this lab. Explain how this would concretely improve the lab by conjecturing possible outcomes.

\newpage
\thispagestyle{plain}
\mbox{}
\newpage

\end{document}